Two-Dimensional Hydrodynamics of a Janus Particle Vesicle

### 2022-02-16 doc/reviews/ResponseToReviewer3.tex

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Petia Vlahovska,
\\ \\
\noindent
We thank you for handling the manuscript and the
Reviewers for carefully evaluating our work. 
The revisions address all the comments and concerns
raised by the Reviewers 
and we believe the result is a significantly improved manuscript.
An itemized list of the specific changes and responses follows.
Changes to the manuscript from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 3}
\comment{\noindent
The manuscript extends the authors’ previous work on modeling
amphiphilic particles in a viscous solvent to modeling amphiphilic Janus
particles suspended in a viscous background flow. The authors adopted
the GMRES iterative method to solve the screened Laplace equation for
hydrophobic attraction. They investigated the inter-monolayer friction
of vesicles formed by amphiphilic Janus particles and corresponding
membrane ruptures in viscous flows, and simulated the spatial migration
dynamics of a vesicle in a parabolic flow and also the hydrodynamics of
two vesicles in shear and extensional flows.
\\ \\
\noindent
This manuscript presents a systematic study of the hydrodynamics of
vesicles formed by amphiphilic Janus particles in viscous flows. It
provides quantitative analysis of the inter-monolayer friction, membrane
permeability and the migration dynamics of soft suspended vesicles. The
topic on hydrodynamics of complex fluids is interesting, and this
research fits the scope of Journal of Fluid Mechanics. Here, I am in a
favor of its publication at some points if the authors can address the
following concerns in the revised manuscript.
}
\begin{itemize}
\item We thank the Reviewer for their positive feedback
  and suggestions which have helped improve the content and presentation of the
  manusript.
%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}
\end{itemize}

\noindent
\comment{{\bf 1.} In section 2.2, the authors defined a repulsion force with an
empirical formula to prevent particle collisions. However, there is no
benchmark test to show that this artificial repulsion force can generate
correct hydrodynamic lubrication. The authors are suggested to justify
and validate the use of the Imposed Forces with comparison to well-known
lubrication forces between particles.}
\begin{itemize}
  \item Response: The repulsive potential we used to prevent overlap of Janus particles is the repulsive Morse potential based on the electrostatic repulsive potential between two negatively (or positively) charged particles immersed in a medium of low electrolyte concentration so that there is a well-defined zeta potential on the charged particle (Coakley {\sl et al.}, 1999, Biophys. J). This repulsive potential has been approximated by the short-range repulsive Lennard-Jones potential (Flormann {\sl et al.}, 2017, Sci. Reports), which has been adopted by Quaife and Young to study the interaction between two membranes in a viscous solvent in Quaife, Veerapaneni and Young, 2019, Phys. Rev. Fluids, where Quaife {\sl et al.} showed that the lubrication hydrodynamics (draining of fluid between two membrane) is well-captured and the scaling of lubrication thin film is recovered.

@@

This is evidence that the lubrication hydrodynamics of the thin film between two particles under the repulsive Morse potential is well captured  if the flow velocity can be accurately calculated in the boundary integral simulations when two particles are sufficiently close to each other and the short-range repulsion is the dominant force.

In this work we used similar numerical techniques to solve the integral equations when some boundaries are quite close to each other.  As the repulsive Morse potential works well to prevent overlapping of particles (provided the time step size is sufficiently small), our previous results in Quaife, Veerapaneni and Young, 2019, Phys. Rev. Fluids gives us confidence in the accuracy of the fluid flow in the thin space between the particles.

\item Change: We added added a paragraph at the end of Section 2.2 describing
  how the lubrication hydrodynamics in a narrow space between boundaries is
  well-captured within the boundary integral formulation.
  Then, in section 4.1 \textit{Model Parameters}, we show quantitatively how the lubrication and
  artificial repulsion are comparable when substituing for our simulation parameters.
\end{itemize}

\noindent
\comment{{\bf 2.} Fig.~3 plots the time evolution of the reduced area in (a) and
the excess length of the bilayer structure in (b). Both show obvious
oscillations with multiple frequencies, which are not as smooth as the
inset of (c) showing one dominant frequency. The authors are suggested
to explain the source of multiple frequencies generated in the time
evolution of $A$ and $\Delta$.}
\begin{itemize}
\item Response: We thank the Reviewer for highlighting this qualitative aspect of
  the curves.

\item Change: We modified the second to last paragraph in Section 4.2.1,
 noting that the frequencies correspond to the tank-treading of the slightly
  polygonal vesicle and individual particles, respectively. 
  Moreover, we scaled the abscissas of Figure 3 to percent, and corrected
  an erroneous scale factor in the time axes. 
\end{itemize}

\noindent
\comment{{\bf 3.} Fig.~6 illustrates the migration process of a JP vesicle in a
parabolic flow, where the moving velocity is 8 nm/ns and the time frame
is 0 to 12 $\mu$s. Given the length scale R = 20 nm, the migration
distance should be $1000 \times R$. However, in the figure, it shows a
migration distance about $4 \times R$. The authors are suggested to
double-check their model parameterization.}
\begin{itemize}
\item Response: Fig.~6 shows 4 snapshots in the time frame from 0 to 12 $\mu$s along with the trajectory of the centriod.

  \item Change: In the caption of Fig.~6,  we now clarify that the horizontal axis 
    represents time and that the vertical axis has been scaled to make the
    migration stand out.

@@

\end{itemize}

\noindent
\comment{{\bf 4.} In Fig.~10, the significant discontinuities in streamlines
across the surface of vesicles are observed, while in most other cases
the streamlines are smooth across the interface of vesicles. The authors
are suggested to describe such discontinuity and provide the
explanation.}
\begin{itemize}
\item Response: We thank the Reviewer for pointing this out.
  This issue occurred due to a limitation of the software used
  to generate streamlines in post-processing.

\item Change: We improved the software and the corrected streamlines now appear in Fig.~11.
  As expected, the streamlines are continuous while their gradient is peicewise continuous
  across the JP vesicle interface.
\end{itemize}

\noindent
\comment{Minor: I read some grammatical errors in the manuscript that
should be corrected, i.e., ``replicate well-know vesicle hydrodynamics
$\ldots$" on page 2, ``$\ldots$ a baseline JP vesicles $\ldots$" on page
8, ``circular vesicles has a Laplace pressure $\ldots$" at Eq.~(4.7).
The authors are suggested to have a thorough read of the manuscript.}
\begin{itemize}
  \item The typo with ``well-know" is corrected, but colored in red
    since it was pointed out by Reviewer 1 as well.

@@

  \item The manuscript now reads
    \begin{quotation}
      $\ldots$ a baseline JP vesicle $\ldots$
    \end{quotation}

  \item The typo with ``has" instead of ``have" is corrected, but
    colored in red since it was pointed out by Reviewer 1.

  \item We have read through the manuscript and done our best to
    remove further grammatical errors.

### 2022-02-16 doc/reviews/ResponseToReviewer2.tex

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Professor Petia Vlahovska,
\\ \\
\noindent
We thank you for handling the manuscript and the
Reviewers for carefully evaluating our work. 
The revisions address all the comments and concerns
raised by the Reviewers 
and we believe the result is a significantly improved manuscript.
An itemized list of the specific changes and responses follows.
Changes to the manuscript from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

### 2022-02-16 doc/main_jfm.tex
main

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
Our simulation studies begin by showing, for the first time, that a JP
suspension with hydrophobic attraction behaves as a tank-treading
vesicle (\cite{Finken08, Shaqfeh11}). The centroid of the baseline,
$58$-body JP vesicle lies at the origin and the background shear flow 
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align} 
is applied for shear rate $\dot\gamma$, and orthogonal unit vectors
$\mathbf{e}_x$ and $\mathbf{e}_y$ for the horizontal and vertical
directions, respectively. We use the dimensionless shear rate $\chi =
\dot \gamma$ (s$^{-1}$) ns.

@@

%updated table
\begin{table}
\caption{Friction Coefficients $b$ (pN ns nm$^{-3}$) \\
}
\centering
\begin{tabular}{c c c c c c c c c c c c }
& & & & & & & $\dot\gamma$  (ns$^{-1}$) & & & &\\
\cline{1-11}\\
  radius ($l_0$) &  $\rho$ ($l_0$) & $\rho_0(l_0)$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
\cline{4-10}\\
& $+ 10 \%$ &     & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  \\ 
& $+ 5 \%$ & & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
0.5 &  2.0 & 0.5    & 0.42 & 0.63 & 0.50   & 0.40  & 0.48  & 0.53 & 0.55 & 0.50 \\   % new
& $- 5 \%$ &  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\ 
\end{tabular} 
\label{table1}
\end{table}

@@

%Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the baseline number of particles is $N_b = 58$. With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
With $-5\%$, $5\%$, and $10\%$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{61,56,53\}$, respectively. }
%
\ReviewerOne{The overall trend shown in Table~\ref{table1} is values of $b$ decreases as $\rho$
decreases and $b$ are}
%over a range of shear rates which is 
in good quantitative agreement with values previously reported in the literature.
Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
\cite{WuoEd06} and \cite{denOtter2007} reported $b = 0.7 \times 10^6$ Pa m$^{-1}$ s  
$=0.7$ pN ns nm$^{-3}$  
and $b = 2.4$  pN ns nm$^{-3}$ for DPPC membranes simulated by MD, respectively. 
Using a more recent version of the Martini force field, \cite{Zgorski2019} 
gives $b = 5.5$ pN ns nm$^{-3}$ for shear rates 0.4 ns$^{-1}$ and higher.
It is understandable that there is uncertainty in the friction coefficients of
Table~\ref{table1}.  The scatter in our data, however, is fully consistent with that calculated
from MD simulations, c.f. the transient rise in values of Table~\ref{table1} and in \cite{Zgorski2019}, Figure 10
for low shear rates. 
%\subsubsection{Membrane Ruptures}
%\begin{figure}
%\centering
%\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%%\includegraphics[height=2in]{N58_rupt_0.pdf}
%%\includegraphics[height=2in]{N58_rupt_200.pdf}
%\\
%%\includegraphics[height=2in]{N58_rupt_400.pdf}
%%\includegraphics[height=2in]{N58_rupt_600.pdf}
%  \caption{\label{figure8} Tank-treading leads to membrane rupture for
%  large shear rates.} 
%\end{figure}
%A temporary fissure or a complete membrane rupture can occur at large
%shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
%when suspended in a shear flow. For $\chi = 0.1$, starting with a
%circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
%background flow and fissures appear in the bilayer structure in multiple
%locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
%ruptured vesicles form two planar micelles which are eventually carried
%off by the flow (Figure~\ref{figure8}d). 
%%
%\ReviewerOne{An emperical numerical study has shown that the critical shear rate for a complete membrane rupture is $\chi=0.0655$. Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.}

@@

\ReviewerOne{An emperical numerical study found that for the baseline parameter set,
the dimensionless, critical shear rate is $\chi_*=0.0655$ so that the membrane ruptured whenever $\chi > \chi_*$
  and did not rupture whenever $\chi < \chi_*.$ 
  Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.
  To further quantify the competition between shear and attraction,
  we found that a 5 \% relative increase in the parameters $\gamma$ and $M$ 
  resulted in a  4.24 \% relative increase in $\chi_*$, from $0.0655$ to $0.0688$.
  A 5 \% decrease in the particle radius $c$ gave a -9.55 \% decrease in $\chi_*$
  and a 10 \% increase in resting length $L_0$ gave a 20.61 \% decrease in critical shear rate $\chi_*$.
  These relative changes suggest that there is dimensionless number $K$ given by 
  \begin{equation}
    \label{eq:CSR}
  \mu \dot\gamma_* = K \frac{\gamma c^2}{\rho L^2}
  \end{equation}
  that relates hydrophobic attraction to the dimensional critical shear rate $\dot \gamma_* = \chi_* \text{ ns}^{-1}$.
  Assuming a characteristic velocity $L\dot \gamma$, the number $K$ relates to the vesicle's capillary number
  $\text{Ca} = K c^2/(\rho L)$. Here $\text{Ca}$ would be approximately $1.7$
  so that surface forces are comparable to viscous forces.  
  There is a related \emph{elastic} capillary number
  $\tilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/\kappa$
  used to characterize rheological properties of lipid bilayer membranes
  where $R_0$ is vesicle radius $\kappa$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
  Setting $\text{Ca}$ and $\tilde{\text{Ca}}$ equal, we can derive
  \[
  \kappa = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
  \]
  which yields $\kappa \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
  value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle placed in a parabolic flow
  drifts toward the central axis. It assumes a slipper shape and
  undergoes tank-treading motion like in the shear flow case. 
 \ReviewerThree{The horizontal dashed line represents time in units of $\mu$s and the vertical axis represents the scaled $y$ position of the centroid of the JP vesicle.}
  The arrows
  on the left illustrate the background flow and the arrows on the right
  show the velocity relative to the vesicle's moving frame. The thick
  black curve plots the distance from the axis as a function of time
  from left to right. The parameters are $v_{max} = 8$~nm ns$^{-1}$,
  $w=10$, and $R_0=20$ nm.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table}
\caption{Stretching Moduli and Permeabilities}
\centering
\begin{tabular}{ c c c |c c| c |c }
 radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (\mathrm{k_BT})$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
\hline      \hline 
 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
%
 \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 5 \%$}  & 185$\pm5$  &  0.0292  \\ 
%
 \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 10 \%$}  & 195$\pm5$  &  0.0294 \\ 
%
 \multicolumn{3}{c|}{$- 5 \%$} & \multicolumn{2}{c|}{same}   & 184$\pm5$  &  0.0283 \\ 
%
 \multicolumn{3}{c|}{$- 10 \%$} & \multicolumn{2}{c|}{same}   & 189$\pm6$  &  0.0252  \\ 
\end{tabular} 
\label{table2}
\end{table}
%

We performed a parametric study of the dependence of $K_A$ and $P$
on model parameters taking into account   
(i) changes in interfacial strength and (ii) changes in size.
Table~\ref{table2} provides the results of stretching moduli $K_A$ and permeabilities $P$ for various cases.
 The baseline setup is shown in the first row.
The next two rows demonstrate the results when the tension related parameters $\gamma$ and $M$ are increased by 5$\%$ and 10$\%$. 
The final two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$
This data comes from Figure \ref{figure2} which  plots the \emph{ratio} of the abscissa and ordinates
used in Figure \ref{figure2part1}c, d. The transformed data are fit by constant functions.

Increases in $\gamma$ and $M$ result in
a commensurate increase in the stretching modulus. 
Permeability, however, is insensitive to simultaneous increases in $\gamma$ and $M$.
To give a detailed explanation for this, the JP system has the potential energy $E = G + H$ where 
\begin{equation}
\label{eq:baseline_energy}
G = \gamma \int_{\Omega} \rho |\nabla \ReviewerTwo{\eta}|^2 + \rho^{-1} \ReviewerTwo{\eta}^2 \,\dif\xx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
       P(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{equation}
Here, $G$ is the hydrophobic attraction potential for the boundary value problem \eqref{eq:SL}--\eqref{eq:SLff},
and $H$ is the repulsion potential.  
For the circular vesicle, total energy depends only on the characteristic inter-particle distance $x$
and has a minimum at $x_0$. 
If $\gamma$ and $M$ are scaled by $c$, 
we can related the scaled energy to that of the baseline case by 
\[E_c(x) = c(G(x) + H(x)).\]
Permeability does not change with like increases in $\gamma$ and $M$
because the critical number for $E_c$, and hence inter-particle separations, are independent to $c$.
The stretching modulus comes from $\frac{d^2E_c}{dx^2}$ and this 
quantity varies proportionally with $c$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
Our simulation studies begin by showing, for the first time, that a JP
suspension with hydrophobic attraction behaves as a tank-treading
vesicle (\cite{Finken08, Shaqfeh11}). The centroid of the baseline,
$58$-body JP vesicle lies at the origin and the background shear flow 
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align} 
is applied for shear rate $\dot\gamma$, and orthogonal unit vectors
$\mathbf{e}_x$ and $\mathbf{e}_y$ for the horizontal and vertical
directions, respectively. We use the dimensionless shear rate $\chi =
\dot \gamma$ ns.

@@

%updated table
\begin{table}
\caption{Friction Coefficients $b$ (pN ns nm$^{-3}$) \\
}
\centering
\begin{tabular}{c c c c c c c c c c c c }
  \hline
& & & & & & $\dot\gamma$  (ns$^{-1}$)& & & & &
  \\
  radius ($l_0$) &  $\rho$ ($l_0$) & $\rho_0(l_0)$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
\cline{4-10}\\
$-5 \%$ & $- 5 \%$ & $-5 \%$  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\
0.5 &  2.0 & 0.5    & 0.42 & 0.63 & 0.50   & 0.40  & 0.48  & 0.53 & 0.55 & 0.50 \\   % new
$+5 \%$ & $+ 5 \%$ & $+ 5 \%$  & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
$+ 10 \%$ & $+ 10 \%$ & $+ 10 \%$    & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  
\end{tabular} 
\label{table1}
\end{table}

@@

%Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the baseline number of particles is $N_b = 58$. With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
With $-5\%$, $5\%$, and $10\%$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{61,56,53\}$, respectively. }
%
\ReviewerOne{The trends in Table~\ref{table1}
  suggest that $b$ decreases with decreasing $\rho$, $\rho_0$, and particle radius.}
Overall, the values for $b$ are 
in good quantitative agreement with values previously reported in the literature.
Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
\cite{WuoEd06} and \cite{denOtter2007} reported $b = 0.7 \times 10^6$ Pa m$^{-1}$ s  
$=0.7$ pN ns nm$^{-3}$  
and $b = 2.4$  pN ns nm$^{-3}$ for DPPC membranes simulated by MD, respectively. 
Using a more recent version of the Martini force field, \cite{Zgorski2019} 
gives $b = 5.5$ pN ns nm$^{-3}$ for shear rates 0.4 ns$^{-1}$ and higher.
It is understandable that there is uncertainty in the friction coefficients of
Table~\ref{table1}.  The scatter in our data, however, is fully consistent with that calculated
from MD simulations, c.f. the transient rise in values of Table~\ref{table1} and in \cite{Zgorski2019}, Figure 10
for low shear rates. 
%\subsubsection{Membrane Ruptures}
%\begin{figure}
%\centering
%\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%%\includegraphics[height=2in]{N58_rupt_0.pdf}
%%\includegraphics[height=2in]{N58_rupt_200.pdf}
%\\
%%\includegraphics[height=2in]{N58_rupt_400.pdf}
%%\includegraphics[height=2in]{N58_rupt_600.pdf}
%  \caption{\label{figure8} Tank-treading leads to membrane rupture for
%  large shear rates.} 
%\end{figure}
%A temporary fissure or a complete membrane rupture can occur at large
%shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
%when suspended in a shear flow. For $\chi = 0.1$, starting with a
%circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
%background flow and fissures appear in the bilayer structure in multiple
%locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
%ruptured vesicles form two planar micelles which are eventually carried
%off by the flow (Figure~\ref{figure8}d). 
%%
%\ReviewerOne{An emperical numerical study has shown that the critical shear rate for a complete membrane rupture is $\chi=0.0655$. Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.}

@@

\ReviewerOne{An emperical numerical study found that for the baseline parameter set,
the dimensionless, critical shear rate is $\chi_*=0.0655$ so that the membrane ruptured whenever $\chi > \chi_*$
  and did not rupture whenever $\chi < \chi_*.$ 
  Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.
  To further quantify the competition between shear and attraction,
  we found that a 5 \% relative increase in the parameters $\gamma$ and $M$ 
  resulted in a  4.24 \% relative increase in $\chi_*$, from $0.0655$ to $0.0688$.
  A 5 \% decrease in the particle radius $c$ gave a -9.55 \% decrease in $\chi_*$
  and a 10 \% increase in resting length $L_0$ gave a 20.61 \% decrease in critical shear rate $\chi_*$.
  These relative changes suggest that there is dimensionless number $K$ given by 
  \begin{equation}
    \label{eq:CSR}
  \mu \dot\gamma_* = K \frac{\gamma c^2}{\rho L^2}
  \end{equation}
  that relates hydrophobic attraction to the dimensional critical shear rate $\dot \gamma_* = \chi_* \text{ ns}^{-1}$.
  Assuming a characteristic velocity $L\dot \gamma$, the number $K$ relates to the vesicle's capillary number
  $\text{Ca} = K c^2/(\rho L)$. Here $\text{Ca}$ would be approximately $1.7$
  so that surface forces are comparable to viscous forces.  
  There is a related \emph{elastic} capillary number
  $\tilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/K_B$
  used to characterize rheological properties of lipid bilayer membranes
  where $R_0$ is vesicle radius $K_B$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
  Setting $\text{Ca}$ and $\tilde{\text{Ca}}$ equal, we can derive
  \[
  K_B = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
  \]
  which yields $K_B \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
  value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle placed in a parabolic flow
  drifts toward the central axis. It assumes a slipper shape and
  undergoes tank-treading motion like in the shear flow case. 
  \ReviewerThree{The horizontal dashed line represents time in units of
    $\upmu$s and the vertical axis represents the scaled $y$ position
    of the centroid of the JP vesicle.}
  The arrows
  on the left illustrate the background flow and the arrows on the right
  show the velocity relative to the vesicle's moving frame. The thick
  black curve plots the distance from the axis as a function of time
  from left to right. The parameters are $v_{max} = 8$~nm ns$^{-1}$,
  $w=10$, and $R_0=20$ nm.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\begin{table}
%\caption{Stretching Moduli and Permeabilities}
%\centering
%\begin{tabular}{ c c c |c c| c |c }
% radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (\mathrm{k_BT})$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$%^{-1}$pN$^{-1}$) \\
%\hline      \hline 
% 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
% \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 5 \%$}  & 185$\pm5$  &  0.0292  \\ 
% \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 10 \%$}  & 195$\pm5$  &  0.0294 \\ 
% \multicolumn{3}{c|}{$- 5 \%$} & \multicolumn{2}{c|}{same}   & 184$\pm5$  &  0.0283 \\ 
% \multicolumn{3}{c|}{$- 10 \%$} & \multicolumn{2}{c|}{same}   & 189$\pm6$  &  0.0252  \\ 
%\end{tabular} 
%\label{table2}
%\end{table}
%

\begin{table}
\caption{Stretching Moduli and Permeabilities}
\centering
\begin{tabular}{ c |c| c |c }
 $k$ & $\lambda$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
\hline    
 1  & 1  & 170$\pm9$   &  0.0296\\ 
%
 1.05 & 1  & 185$\pm5$  &  0.0292  \\ 
%
 1.10 & 1  & 195$\pm5$  &  0.0294 \\ 
%
 1 & 0.95  & 184$\pm5$  &  0.0283 \\ 
%
 1  & 0.9   & 189$\pm6$  &  0.0252  \\ 
\end{tabular} 
\label{table2}
\end{table}
%

We performed a parametric study of the dependence of $K_A$ and $P$
on model parameters taking into account   
(i) changes in interfacial strength and (ii) changes in size.
Table~\ref{table2} provides the results of stretching moduli $K_A$ and permeabilities $P$ for various cases.
The baseline setup is shown in the first row.
The next two rows demonstrate the results when the tension related parameters $\gamma$ and $M$ are increased by 5$\%$ and 10$\%$. 
The parameter $k$ is used to scale the force paramaters $\gamma, M \to k\gamma, kM$.
The final two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$
The parameter $\lambda$ is used to simultaneously scale length parameters;
$\rho, \rho_0, c \to \lambda \rho, \lambda \rho_0, \lambda c$.
This data comes from Figure \ref{figure2} which  plots the \emph{ratio} of the abscissa and ordinates
used in Figure \ref{figure2part1}c, d. The transformed data are fit by constant functions.

Increases in $\gamma$ and $M$ result in
a commensurate increase in the stretching modulus. 
Permeability, however, is insensitive to simultaneous increases in $\gamma$ and $M$.
To give a detailed explanation for this, the JP system has the potential energy $E = G + H$ where 
\begin{equation}
\label{eq:baseline_energy}
G = \gamma \int_{\Omega} \rho |\nabla \ReviewerTwo{\eta}|^2 + \rho^{-1} \ReviewerTwo{\eta}^2 \,\dif\xx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
       P(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{equation}
Here, $G$ is the hydrophobic attraction potential for the boundary value problem \eqref{eq:SL}--\eqref{eq:SLff},
and $H$ is the repulsion potential.  
For the circular vesicle, total energy depends only on the characteristic inter-particle distance $x$
and has a minimum at $x_0$. 
If $\gamma$ and $M$ are scaled by a parameter $k$, 
we can related the scaled energy to that of the baseline case by 
\[E_k(x) = k(G(x) + H(x)).\]
Permeability does not change with like increases in $\gamma$ and $M$
because the critical number for $E_k$, and hence inter-particle separations, are independent to $k$.
The stretching modulus comes from $\frac{d^2E_k}{dx^2}$ and this 
quantity varies proportionally with $k$.
